Supplement for: Carbon cycling in mature and regrowth forests globally: a macroecological synthesis based on the global Forest Carbon (ForC) database

### 2020-09-29 manuscript/ERL_global_C_SI.Rmd
knit in new results

  knitr::include_graphics("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/ForC-db/ForC/figures/age_trends/ANPP_woody_stem.png")
```

@@

  knitr::include_graphics("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/ForC-db/ForC/figures/age_trends/BNPP_root.png")
```

@@

  knitr::include_graphics("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/ForC-db/ForC/figures/age_trends/BNPP_root_coarse.png")
```

@@

  knitr::include_graphics("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/ForC-db/ForC/figures/age_trends/BNPP_root_fine.png")
```

@@

  knitr::include_graphics("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/ForC-db/ForC/figures/age_trends/R_auto_root.png")
```

@@

  knitr::include_graphics("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/ForC-db/ForC/figures/age_trends/biomass_ag_foliage.png")
```

>>>>

  knitr::include_graphics("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/ForC-db/ForC/figures/age_trends/ANPP_stem.png")
```

@@

  knitr::include_graphics("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/ForC-db/ForC/figures/age_trends/BNPP.png")
```

@@

  knitr::include_graphics("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/ForC-db/ForC/figures/age_trends/BNPP_coarse.png")
```

@@

  knitr::include_graphics("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/ForC-db/ForC/figures/age_trends/BNPP_fine.png")
```

@@

  knitr::include_graphics("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/ForC-db/ForC/figures/age_trends/R_root.png")
```

@@

  knitr::include_graphics("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/ForC-db/ForC/figures/age_trends/biomass_foliage.png")
```
